SoK: Transparent Dishonesty. Front-running attacks on Blockchain.

### 2018-12-05 frontrunning/Latex/sections/abstract.tex
[frontrunning] few edits here and there

We consider \textit{front-running} to be a course of action where an entity benefits from prior access to privileged market information about upcoming transactions and trades. Front-running has been an issue in traditional financial instrument markets since the 1970's. With the advent of the blockchain technology, front-running resurfaced in new forms we explore here, due to blockchain's decentralized and transparent nature.
In this paper, we consider instances of front-running across the top 25 decentral applications (DApps) deployed on Ethereum. Additionally, we carry out a detailed analysis of \textsf{Status.im} initial coin offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases. Finally, we introduce a framework for categorizing proposed solutions to front-running and examine the applicability to the identified issues.

\end{abstract}

>>>>

We consider \textit{front-running} to be a course of action where an entity benefits from prior access to privileged market information about upcoming transactions and trades. Front-running has been an issue in traditional financial instrument markets since the 1970's. With the advent of the blockchain technology, front-running resurfaced in new forms we explore here, due to blockchain's decentralized and transparent nature.
In this paper, we draw from a scattered body of knowledge and instances of front-running across the top 25 decentral applications (DApps) deployed on Ethereum. Additionally, we carry out a detailed analysis of \textsf{Status.im} initial coin offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases. Developers don't have the mindset to design DApps with front-running in mind. This is an attempt to bring forward the subject and make them more aware of these type of attacks. Finally, we introduce a framework for categorizing proposed solutions to front-running and examine the applicability to the identified issues. 
\end{abstract}

### 2018-12-05 frontrunning/Latex/sections/paper.tex
[frontrunning] few edits here and there

The mechanics of front-running works on all DApps but front-running is not necessarily beneficial, depending on the DApp's internal logic and/or as any mitigations it might implement. Therefore, DApps need to be studied individually or in categories. This paper is a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps) from each category of the top 25 most active, based on user activity.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service). We also study initial coin offerings (ICOs), which by happenstance, did not appear in the top 25 on our sample day. After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico,li2018initial}. ICOs started to experiment with different \textit{fair} capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}. We show empirical evidence of a miner purchasing tokens ahead of other users in Status.im. Finally, proposals to eliminate or mitigate front-running from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them in the last section.

@@

>>>>

The mechanics of front-running works on all DApps but front-running is not necessarily beneficial, depending on the DApp's internal logic and/or as any mitigations it might implement. Therefore, DApps need to be studied individually or in categories. In this paper we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps) from each category of the top 25 most active, based on user activity.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service). We also study initial coin offerings (ICOs), which by happenstance, did not appear in the top 25 on our sample day. After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico,li2018initial}. ICOs started to experiment with different \textit{fair} capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}. We show empirical evidence of a miner purchasing tokens ahead of other users in Status.im. Finally, proposals to eliminate or mitigate front-running from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them in the last section.

@@

% we can say other illegal activities in the tranditional system, such as wash trading, ... (notes from AMF) could fall under our definition of front running on blockchain apps, as the transparency and public nature of the transactions could result in any actor to be involved in such trades? does it make sense?
